### 2019-04-16 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits.tex
J'arriverai jamais à finir... trop chiant.

\paragraph{Outline.}
%
The rest of the chapter is organized as follows.
We introduce the multi-player bandit model with three feedback levels in Section~\ref{sec:5:model}, and give a new regret lower bound in Section~\ref{sec:5:lowerbound}.
The \RandTopM, \MCTopM{} and \Selfish{} algorithms are introduced in Section~\ref{sec:5:algorithms},
for which we present our theoretical analysis in Section~\ref{sec:5:upperbounds}.
Finally, the result of our experimental study reported in Section~\ref{sec:5:experiments}.
% and finally Section~\ref{sec:5:conclusion} concludes.

@@

% FIXME
\begin{framed}
  \textbf{\textcolor{red}{Warning}.}
  The regret lower bound given in \cite{Besson2018ALT} is not applicable to any algorithm,
  as it was discovered by Etienne Boursier and Vianney Perchet, as they explain in Section~2.4 in \cite{BoursierPerchet18}.
  The proof we gave in the Appendix of our paper \cite{Besson2018ALT} was wrong in just one step,
  but the results stated in the section are now correct,
  thanks to the modifications proposed by Emilie Kaufmann and Abbas Mehrabian in Appendix~E of \cite{KaufmannAbbas19}.
  The cost for this modification is to restrict the lower-bound to a smaller class of algorithms, which contains both \RhoRand{} and our two proposals \RandTopM{} and \MCTopM{} but not the two algorithms proposed SIC-MMAB from \cite{BoursierPerchet18} and Multiplayer Explore-then-Commit (M-ETC) from \cite{KaufmannAbbas19}.
\end{framed}
% FIXME

@@

  Now we can decompose the sum on $t=1,\dots,T$ with the use of consecutive sequences,
  \begin{align}
    \E_{\mu}[N_2^j(t)]
    &= \E_{\mu}\left[ \sum_{t=1}^T \indic{\left(I_2^j(t)\right)} \right]
    =
    \E_{\mu}\left[ \sum_{i=1}^{n(T)} \left( \sum_{t=\theta_i}^{\tau_i - 1} 1 + \sum_{t=\tau_i}^{\theta_{i+1} - 1} 0 \right) \right]
    =
    \E_{\mu}\left[ \sum_{i=1}^{n(T)} (\tau_i - \theta_i) \right].
    \intertext{Both $n(T)$ and $\tau_i - \theta_i \geq 0$ have finite averages for any $i$ (as $\tau_i - \theta_i \leq T$), and $n(T)$ is a \emph{stopping time} with respect to the past events (that is, $\cF^j_T$), and so we can obtain a decomposition with two terms $(\alpha)$ and $(\beta)$:}
    % so we can use Wald's Lemma \citep{Wald45}
    &\leq \underbrace{\E_{\mu}\left[ n(T) \right]}_{(\alpha)} \times \underbrace{\max_{i\in\N} \E_{\mu}\left[ \tau_i - \theta_i \right]}_{\beta}.
    % = (\alpha) \times (\beta).
  \end{align}

>>>>

\paragraph{Outline.}
%
The rest of the chapter is organized as follows.
We introduce the multi-player bandit model with three feedback levels in Section~\ref{sec:5:model}, and give a new regret lower bound in Section~\ref{sec:5:lowerbound}.
The \RandTopM, \MCTopM{} and \Selfish{} algorithms are introduced in Section~\ref{sec:5:algorithms},
for which we present our theoretical analysis in Section~\ref{sec:5:upperbounds}.
The result of our experimental study reported in Section~\ref{sec:5:experiments}.
Finally, we present in Section~\ref{sec:5:literatureReviewOtherModels} a review of the recent literature which studies variants of the model presented in this Chapter.
% and finally Section~\ref{sec:5:conclusion} concludes.

@@

% FIXME
\begin{framed}
  \textbf{\textcolor{red}{Warning}.}
  The regret lower bound given in \cite{Besson2018ALT} is not applicable to any algorithm,
  as it was discovered by Etienne Boursier and Vianney Perchet, as they explain in Section~2.4 in \cite{BoursierPerchet18}.
  The proof we gave in the Appendix of our paper \cite{Besson2018ALT} was wrong in just one step,
  but the results stated in this section are now correct,
  thanks to the modifications proposed by Emilie Kaufmann and Abbas Mehrabian in Appendix~E of \cite{KaufmannAbbas19}.
  The cost for this modification is to restrict the lower-bound to a smaller class of algorithms, which contains both \RhoRand{} and our two proposals \RandTopM{} and \MCTopM{} but not the two algorithms proposed SIC-MMAB from \cite{BoursierPerchet18} and Multiplayer Explore-then-Commit (M-ETC) from \cite{KaufmannAbbas19}.
\end{framed}
% FIXME

@@

  Now we can decompose the sum on $t=1,\dots,T$ with the use of consecutive sequences,
  \begin{align}
    \E_{\mu}[N_2^j(t)]
    &= \E_{\mu}\left[ \sum_{t=1}^T \indic{\left(I_2^j(t)\right)} \right]
    =
    \E_{\mu}\left[ \sum_{i=1}^{n(T)} \left( \sum_{t=\theta_i}^{\tau_i - 1} 1 + \sum_{t=\tau_i}^{\theta_{i+1} - 1} 0 \right) \right]
    =
    \E_{\mu}\left[ \sum_{i=1}^{n(T)} (\tau_i - \theta_i) \right].
    \intertext{Both $n(T)$ and $\tau_i - \theta_i \geq 0$ have finite averages for any $i$ (as $\tau_i - \theta_i \leq T$), and $n(T)$ is a \emph{stopping time} with respect to the past events (that is, $\cF^j_T$), and so we can obtain a decomposition with two terms $(\alpha)$ and $(\beta)$:}
    % so we can use Wald's Lemma \citep{Wald45}
    &\leq \underbrace{\E_{\mu}\left[ n(T) \right]}_{(\alpha)} \times \underbrace{\max_{i\in\N} \E_{\mu}\left[ \tau_i - \theta_i \right]}_{(\beta)}.
    % = (\alpha) \times (\beta).
  \end{align}

### 2019-04-16 2-Chapters/5-Chapter/chapter5.tex
J'arriverai jamais à finir... trop chiant.

\TODOL{
    Pour chaque extension présentée ci dessous, je veux suivre la même organisation :

@@

\TODOL{Explain why the problem is MUCH easier if we have before hand these unique ID!}
If the $M$ players each have a unique ID, then a simple explore-then-commit algorithm running on top of a round-Robin phase can achieve order-optimal regret. Without giving more details, we let the interested refer to what is is explained for the RR-SW-UCB\# algorithm in \cite{WeiSrivastava18Distributed} and the algorithms presented in \cite{DarakHanawal18,JoshiKumar2018,KumarDarak2019}.

@@

@@

An interesting extension is thus to limit the communication between players, either to a small number of bits, or just one bit.
We do not review papers that study this model, because the recent work \cite{BoursierPerchet18} introduced the ``communication trick'', that essentially allow any player to send one bit to all the others, at some pre-agreed time steps, with no modification on the model.
Thanks to this ``communication trick'', recent research efforts have been more focus on studying the basic model --without explicit communications between players--, while proposing algorithms that can rely on some communication between players.
This trick essentially use the fact that the players share a synchronized time, thus they can use a collision as a way to directly exchange one bit of information between two players.
This process is slow and not efficient, as all but two players must do nothing when player $i$ is sending a bit to player $j$, but it does build a communication protocol in the model without explicit communication between players.
This ``communication trick'' is used for instance in \cite{KaufmannAbbas19}.
We let the interested reader refer to these last two works \cite{BoursierPerchet18,KaufmannAbbas19} as they are both solid, and well explained.

>>>>

\TODOL{
    Pour les extension présentées ici, je veux suivre la même organisation :

@@

If the $M$ players each have a unique ID, then a simple explore-then-commit algorithm running on top of a round-Robin phase can achieve order-optimal regret.
If the players know the time horizon $T$, then fix a confidence level $\delta$. For the first $T_0$ time steps, the $M$ players will use a simple round-Robin game, using their (unique) ID to stay orthogonal: player $j$ starts at arm $j$, then $j+1$, then cycle in $\{1,\dots,K\}$. They encounter no collision in these time steps, and then user $j$ targets the $j$-th best arm among the set of $M$-best arm.
If $T_0$ is large enough, all players have built the same estimate of the ranking of the arms (and not only correctly identified the set of $M$-best arms), with high probability (at least $\delta$), and thus they will also encounter no collision and no regret from after time $T_0$.
The mean regret of such approach is easily bounded by $R_T \leq M T_0 + (1 - \delta) (T - T_0)$, so by using $\delta = 1-1/T$, $R_T = \bigO{T_0}$.
By calibrating $T_0$ based on $\delta$ (which needs prior knowledge of $T$) and the minimal gap $\Delta$ between \Mbest{} and \Mworst, one can show, using similar arguments as used by \cite{Rosenski16} for the Musical Chair policy, that with large probability a constant regret is obtained. A logarithmic regret can be obtained from the same bound, proving the order-optimality of this simple approach, if we assume that user $j$ knows it is user number $j$.
%
Without giving more details, we let the interested refer to what is is explained for the algorithms presented in \cite{DarakHanawal18,JoshiKumar2018,KumarDarak2019}.
%
These works assume a prior knowledge of $\Delta$, or other measures of the difficulty of the problem, and as such we do not.
FIXME
\TODOL{FIXME écrire ça sans être fini}

@@

The recent work \cite{BoursierPerchet18} proposed an idea they called the ``communication trick''.
It essentially allow any player to send one bit to all the others, at some pre-agreed time steps, with no modification on the model.
Thanks to this ``communication trick'', recent research efforts have been more focus on studying the basic model --without explicit communications between players--, while proposing algorithms that can rely on some communication between players.
This trick essentially use the fact that the players share a synchronized time, thus they can use a collision as a way to directly exchange one bit of information between two players.
This process is slow and not efficient, as all but two players must do nothing when player $i$ is sending a bit to player $j$, but it does build a communication protocol in the model without explicit communication between players.
This ``communication trick'' is used for instance in \cite{KaufmannAbbas19}.
We let the interested reader refer to these last two works \cite{BoursierPerchet18,KaufmannAbbas19} as they are both solid, and well explained

@@

An interesting extension is thus to limit the communication between players, either to a small number of bits, or just one bit.
We do not review papers that study this model, because the recent work \cite{BoursierPerchet18} introduced the ``communication trick''.
Recent research efforts have been more focus on studying the basic model --without explicit communications between players--, while proposing algorithms that can rely on some communication between players.
This ``communication trick'' is used for instance in \cite{KaufmannAbbas19}.
Due to space constraint, we let the interested reader refer to these last two works \cite{BoursierPerchet18,KaufmannAbbas19} as they are both solid, and well explained.
